Need a good title.

### 2017-12-08 ms.tex
fixed formula 6 in ms

\ml{$Z^{C}$ = $phyZ^{T}$ * Z}

@@

\begin{equation}
Z^{C}_{i} = (BS \bigotimes I_{q_i \times s})^T Z_{i} ,
\end{equation}

where $BS$ is an $b \times s$ matrix of branch--species relations; $I$ is an identity matrix size $q_i \times s$; $q_i$ is the number of columns contributed by $Z_i$; s is the number of sites; and  $\bigotimes$ is the Kronecker product \ml{cite kronecker}.

>>>>

@@

\begin{equation}
Z^{C}_{i} = Z_{i}(SB \bigotimes I_{p_i \times s}) ,
\end{equation}

\ml{double check if $l and p$ are the same with lme4}

where $SB$ is an $l \times b$ matrix of species--branch relations; $I$ is an identity matrix size $p_i \times s$; $p_i$ is the number of columns contributed by $Z_i$; s is the number of sites; and  $\bigotimes$ is the Kronecker product \ml{cite kronecker}.
